%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/dongyanli//}{\Large Dongyan Li}} & Email : \href{mailto:lidongyan1988@gmail.com}{lidongyan1988@gmail.com}\\
  \href{https://www.linkedin.com/in/dongyanli//}{https://www.linkedin.com/in/dongyanli/} & Mobile : +1-312-806-6031 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {DePaul University}{Chicago, IL, U.S.}
      {Master of Science in Computer Science;  GPA: 4.00}{Sep. 2014 – May. 2017}
    \resumeSubheading
      {DePaul University}{Chicago, IL, U.S.}
      {Master of Science in Accounting; GPA: 3.79}{Sep. 2012 – Sep. 2014}
    \resumeSubheading
      {Nanjing University}{Nanjing, Jiangsu, China}
      {Bachelor of Arts in International Economics and Trade; GPA: 3.7}{Sep. 2007 – June. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {LivePerson Inc.}{Remote}
      {Senior Software Development Engineer}{Mar 2022 - Current}
      \resumeItemListStart
        \resumeItem{Workforce Management}
          {Building new connectors to third party vendors.}
      \resumeItemListEnd

    \resumeSubheading
      {StoneX Group Inc.}{Chicago, IL}
      {Senior Data Engineer}{Jan 2020 - Mar 2022}
      \resumeItemListStart
        \resumeItem{Data Platform}
          {Created the entire data platform inside the team using Docker and Kubernetes; made all the back-office system data available through a single API service. Saved millions of dollar and greatly improved customer satisfaction.}
        \resumeItem{Performance Optimization}
          {Instrumented all the services and query engines with distributed tracing; analysed performance bottleneck; reduced 500ms response time for services.}
        \resumeItem{Real-time Feeder}
          {Developed an application which feeds real-time trading data into an external risk evaluation system; achieved 100\% data coverage and 10 seconds max delay.}
        \resumeItem{CI/CD}
          {Wrapped up all test scripts, build and local development command for all the services into Gradle tasks; Converted Azure Pipelines to use Gradle to build and release. Improved developer efficiency and reduced onboarding time.}
      \resumeItemListEnd

    \resumeSubheading
      {StoneX Group Inc.}{Chicago, IL}
      {Data Engineer}{May 2017 - Jan 2020}
      \resumeItemListStart
        \resumeItem{Dremio}
          {Deployed, maintained and optimized backbone data query engine Dremio; later migrated to Kubernetes environment; achieved 0 non-scheduled down time and ability to auto scale up and down.}
        \resumeItem{API Service}
          {Developed OpenAPI REST API service using Python Flask on top of data query engine, used by 6 teams across the company.}
        \resumeItem{Web UI}
          {Developed web application using Angular to showcase REST API service. Convinced 2 outside teams to use the API services}
      \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, Java, C++, SQL, JavaScript, Scala}
   }
 \resumeSubHeadingListEnd
 
 \resumeSubHeadingListStart
   \item{
     \textbf{Tools and Frameworks}{: Apache Airflow, Apache Kafka, Docker, Apache Spark, Kubernetes, Angular,
Envoy Proxy, Apache Camel, Jaeger Tracing, Flask, Spring Boot, Rancher, Helm}
   }
 \resumeSubHeadingListEnd
 
  \resumeSubHeadingListStart
   \item{

     \textbf{Datebase}{: Dremio, SQL Server, PostegreSQL, RocksDB, LevelDB
}
   }
 \resumeSubHeadingListEnd
 
   \resumeSubHeadingListStart
   \item{
     \textbf{Courses}{: Data Structures I II, Algorithm I II, Computer Systems I II, Distributed System, Optimized C++
}

   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
